Analysis of Climate Sensitivity using HadAM3

### 2014-04-27 article.tex
Fill in most of appendix with required info.
Finish of appendix.

\section{Required output}

\begin{enumerate}
    \item first
    \item first
    \item first
    \item second
    \item second
\end{enumerate}

>>>>

\section{Additional information}

N.B. more decimal points quoted than required for detailed numerical comparison.

\begin{enumerate}
    \item \textbf{username on \texttt{puma.nerc.ac.uk}}: UCL3
    \item \textbf{simulation id}: xjksa
    \item \textbf{simulation scenario}: 2x\ce{CO2}
    \item \textbf{\ce{CO2} level of scenario}: \SI{692.1}{ppm}
    \item \textbf{global annual average surface temperature}: \SI{277.859}{K}
    \item \textbf{$G_{2x\ce{CO2}}$}: \SI{3.71}{W.m^{-2}}
    \item \textbf{global annual average surface net flux in control}: \SI{10.102}{W.m^{-2}}
    \item \textbf{Transient Climate Response (TCR)}: \SI{2.044}{K}
    \item \textbf{$\Delta T^{eff}_{2x\ce{CO2}}$}: \SI{2.85}{W.m^{-2}.K^{-1}}
    \item \textbf{RMS surface temperature bias in DJF from control}: \SI{3.943}{K} % TODO: not sure about this one at all.
\end{enumerate}
